### 2014-03-28 ApTranscriptome_TR.Rmd
Changed RxNseq function to perform robust regression using lmrob. Had to use supressWarnings() so messages from lmrob did not prevent ddply from running across all transcripts.
Updates - trying to get RxNseq to work with lmrob. Problems with using 'anova' on exact model fits.

# identify responsive transcripts using robust regression
testdata <- TPM.dt.sub[23:44,]

RxNout <- RxNseq(f = testdata, model = model, threshold = 0.05)

>>>>

# identify responsive transcripts using robust regression
RxNout <- RxNseq(f = TPM.dt.sub, model = model, threshold = 0.05)

RxNout <- RxNseq(f = test, model = model, threshold = 0.05)

## debug
        lmrob.out345 <- suppressWarnings(eval(parse(text = paste("lmrob(", model, ", setting = 'KS2011', data = piece345)", sep = ""))))
